### 2023-01-25 manuscript.Rmd
Get rid of `->` assignment

# Compute number of objects per condition for each participant
with(trials, table(participant_id, condition)) %>%
  `/`(3) %>%
  as.data.frame.matrix() %>%
  rownames_to_column("subject_id") -> objects_per_condition

@@

```{r, mixed_models, include=FALSE}
# Filter relevant conditions for the main analysis
trials %>%
  filter(condition %in% c("Informed", "Uninformed", "Exclude_informed")) %>%
  droplevels() -> trials

# Contrast coding for phase
cbind(
  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
) %>%
  t() %>%
  ginv() -> contrasts(trials$phase)

# Contrast coding for condition
cbind(
  c(`Informed` = 1, `Uninformed` = -1, `Exclude_informed` = 0),
  c(`Informed` = 1, `Uninformed` = 0, `Exclude_informed` = -1)
) %>%
  t() %>%
  ginv() -> contrasts(trials$condition)

@@

  # Fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials) %>%
    set_names(deps) -> models

@@

# Extract relevant statistics to print in the main text
map(models, function(model) as_tibble(model$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`) -> anova_table
map(models, function(model) as_tibble(model$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table
```

@@

```{r, control_analysis, include=FALSE}
# Filter relevant conditions for the control analysis
conditions_control <- c("Informed", "Exclude_informed")
trials %>%
  mutate(condition = factor(condition, levels = conditions_control)) %>%
  drop_na() -> trials_control

# Contrast coding for phase
cbind(
  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
) %>%
  t() %>%
  ginv() -> contrasts(trials_control$phase)

# Contrast coding for condition
cbind(c(`Informed` = 1, `Exclude_informed` = -1)) %>%
  t() %>%
  ginv() -> contrasts(trials_control$condition)

@@

  # Fit the model for each ERP component
  map(deps, fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps) -> models_control

@@

# Extract relevant statistics to print in the main text
map(models_control, function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`) -> contrast_table_control
```

>>>>

# Compute number of objects per condition for each participant
objects_per_condition <- with(trials, table(participant_id, condition)) %>%
  `/`(3) %>%
  as.data.frame.matrix() %>%
  rownames_to_column("subject_id")

@@

```{r, mixed_models, include=FALSE}
# Filter relevant conditions for the main analysis
trials <- trials %>%
  filter(condition %in% c("Informed", "Uninformed", "Exclude_informed")) %>%
  droplevels()

# Contrast coding for phase
contrasts(trials$phase) <- cbind(
  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
) %>%
  t() %>%
  ginv()

# Contrast coding for condition
contrasts(trials$condition) <- cbind(
  c(`Informed` = 1, `Uninformed` = -1, `Exclude_informed` = 0),
  c(`Informed` = 1, `Uninformed` = 0, `Exclude_informed` = -1)
) %>%
  t() %>%
  ginv()

@@

  # Fit the model for each ERP component
  models <- map(deps, fit_mixed_models, formula = form, data = trials) %>%
    set_names(deps)

@@

# Extract relevant statistics to print in the main text
anova_table <- models %>%
  map(function(model) as_tibble(model$anova, rownames = "effect")) %>%
  bind_rows(.id = "component") %>%
  rename(f_value = `F value`, p_value = `Pr(>F)`)
contrast_table <- models %>%
  map(function(model) as_tibble(model$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`)
```

@@

```{r, control_analysis, include=FALSE}
# Filter relevant conditions for the control analysis
conditions_control <- c("Informed", "Exclude_informed")
trials_control <- trials %>%
  mutate(condition = factor(condition, levels = conditions_control)) %>%
  drop_na()

# Contrast coding for phase
contrasts(trials_control$phase) <- cbind(
  c(`Pre-insight` = -1, `Insight` = 1, `Post-insight` = 0),
  c(`Pre-insight` = 0, `Insight` = -1, `Post-insight` = 1)
) %>%
  t() %>%
  ginv()

# Contrast coding for condition
contrasts(trials_control$condition) <- cbind(
  c(`Informed` = 1, `Exclude_informed` = -1)
) %>%
  t() %>%
  ginv()

@@

  # Fit the model for each ERP component
  models_control <- deps %>%
    map(fit_mixed_models, formula = form, data = trials_control) %>%
    set_names(deps)

@@

# Extract relevant statistics to print in the main text
contrast_table_control <- models_control %>%
  map(function(mod) as_tibble(mod$contrasts)) %>%
  bind_rows(.id = "component") %>%
  rename(t_value = `t.ratio`, p_value = `p.value`)
```
